Algorithmic Approaches to Match Degraded Land Impressions

### 2017-10-21 degraded-paper.Rmd
fig 13 ...

ggplot(data = final_result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~method, nrow = 4, labeller = labeller(method = mypaste)) +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.background = element_rect(colour="grey75"),
          axis.text.y = element_blank(),
          axis.title.y = element_blank())
```

>>>>

ggplot(data = final_result, aes(x = match, y = score, fill = match)) +
    geom_boxplot() +
    coord_flip() +
    facet_wrap(~method, nrow = 4, labeller = labeller(method = mypaste)) +
    scale_fill_brewer("Bullet Land Pairs", palette="Paired") +
    theme_bw() +
    theme(legend.background = element_rect(colour="grey75"),
          axis.text.y = element_blank(),
          axis.title.y = element_blank()) +
  theme(legend.position="none") +
  annotate("text", x=2.25, y= 0.8, label="Known matches (KM)", hjust=1, colour="grey40") +
  annotate("text", x=0.75, y= 0.05, label="Known non-matches (KNM)", hjust=0, colour="grey40")
```
